weight_analyses

### 2023-03-22 smelt_2019_winterspring/manuscript_weight_length_k_survival.Rmd
Updated weight length K plot to include a little more on the y axis

## Length-Weight-CF Figures
```{r}
# Summarize mean, sd, median, n for Pre and Post Length and Width
Cagedata <- Cagetype_CF %>%
  na.omit() %>%
  filter(Cage!="FCCL1") %>%
  filter(Cage!="FCCL2") %>%
  group_by(Site, Mesh)%>%
  summarize(
    PreL_Mean = mean(Pre_FL_cm),
    PreL_sd = sd(Pre_FL_cm),
    PreL_median = median(Pre_FL_cm),
    PoL_Mean = mean(Post_FL_cm),
    PoL_sd = sd(Post_FL_cm),
    PoL_median = median(Post_FL_cm), 
    PreW_Mean = mean(Pre_Weight_g),
    PreW_sd = sd(Pre_Weight_g),
    PreW_median = median(Pre_Weight_g),
    PoW_Mean = mean(Post_Weight_g),
    PoW_sd = sd(Post_Weight_g),
    PoW_median = median(Post_Weight_g),  N = n()) %>%
    mutate(delta.Length = round(PoL_Mean - PreL_Mean,2)) %>%
  mutate(delta.weight = round(PoW_Mean - PreW_Mean,2)) %>%
  ungroup()
```

@@

@@

Survival rate
```{r}
surv_RV %>%
  ungroup() %>%
  filter(Cage != "FCCL1") %>%
  summarize(meanRate = mean(rate),
            n = n(),
            seRate = sd(rate)/n)
```

@@

@@

survival_DWSC <- Cagetype_survival_DWSC %>%
  mutate(Cage = factor(Cage),
         fSurvived = factor(Survived),
         Survived = as.numeric(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))%>%
  group_by(Site, Mesh, Cage) %>%
  summarize(Survived = sum(Survived),
            n= n()) %>%
  mutate(rate = Survived/n*100)
```

>>>>

## Length-Weight-CF Figures
```{r}
# Summarize mean, sd, median, n for Pre and Post Length and Width
Cagedata <- Cagetype_CF %>%
  na.omit() %>%
  filter(Cage!="FCCL1") %>%
  filter(Cage!="FCCL2") %>%
  group_by(Site, Mesh)%>%
  summarize(
    PreL_Mean = mean(Pre_FL_cm),
    PreL_sd = sd(Pre_FL_cm),
    PreL_median = median(Pre_FL_cm),
    PoL_Mean = mean(Post_FL_cm),
    PoL_sd = sd(Post_FL_cm),
    PreL_Min = min(Pre_FL_cm), 
    PreL_Max = max(Pre_FL_cm),
    PoL_median = median(Post_FL_cm), 
    PreW_Mean = mean(Pre_Weight_g),
    PreW_sd = sd(Pre_Weight_g),
    PreW_median = median(Pre_Weight_g),
    PoW_Mean = mean(Post_Weight_g),
    PoW_sd = sd(Post_Weight_g),
    PoW_median = median(Post_Weight_g),  N = n()) %>%
    mutate(delta.Length = round(PoL_Mean - PreL_Mean,2)) %>%
  mutate(delta.weight = round(PoW_Mean - PreW_Mean,2)) %>%
  ungroup()
```

@@

# Calculate sample sizes for alive and dead
surv_RV <- Cagetype_s %>%
  filter(Site == "RV") %>%
  group_by(Site, Cage, Mesh)%>%
  summarize(
    Alive = n(),
    Dead = 64-n()
  )

@@

Survival rate
```{r}
survival_RV %>%
  ungroup() %>%
  group_by(Mesh) %>%
  summarize(meanRate = mean(rate),
            n = n(),
            seRate = sd(rate)/sqrt(n))
```

@@

surv_DWSC <- Cagetype_s %>%
  filter(Site == "DWSC") %>%
  group_by(Site, Cage, Mesh)%>%
  summarize(
    Alive = n(),
    Dead = 60-n()
  )

@@

survival_DWSC <- Cagetype_survival_DWSC %>%
  mutate(Cage = factor(Cage),
         fSurvived = factor(Survived),
         Survived = as.numeric(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))%>%
  group_by(Site, Mesh, Cage) %>%
  summarize(Survived = sum(Survived),
            n= n()) %>%
  mutate(rate = Survived/n*100)

Survival rate
```{r}
survival_DWSC %>%
  ungroup() %>%
  group_by(Mesh) %>%
  summarize(meanRate = mean(rate),
            n = n(),
            seRate = sd(rate)/sqrt(n))
```
